---
title: "Survey on return intention & perception of Syrian Refugees in Egypt, Iraq and Jordan \n Preliminary exploration of results - draft not for distribution - "
author: "Prepared by UNHCR DOiA"
date: "Amman, `r Sys.Date()`"
output: 
  word_document: 
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: yes
    toc_depth: 2
    reference_docx: style-unhcr-portrait.docx
    
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
setwd("D:/R-project/intention")
source("code/1-loaddata.R")
library("gplots")

library("corrplot")
library("graphics")
# install.packages("vcd")
library("vcd")



```



# Analysis of Correlation

## Governorate of Origin

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
library("corrplot")
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$COO_L1)



if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")

corrplot(chisq$residuals, is.cor = FALSE)
```

## Case Size

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$size)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Country Asylum

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$CountryAsylum)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Year Arrival

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$YearArrivalCategory)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Female ratio

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$female.ratio)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Dependency

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$dependency)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Ethnicity

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$dem_ethnCat)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occupation

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$occupationcat)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Marrital Status

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$dem_marriagecat)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```


## Average Age

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
data$AVG_Age1 <- cut(as.integer(data$AVG_Age),5)
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$AVG_Age1)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```


## Occurence of needs

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}
## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$needs)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```


## Occurence in the household of person At.Risk

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$At.Risk <- as.character(data$At.Risk)
data$At.Risk[is.na(data$At.Risk)] <- "No"
chisq <- chisq.test(data$group_intro.goingback, as.factor(data$At.Risk))
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE, main="Occurence in the household of person At.Risk")
```

## Occurence in the household of person Child.Labour

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Child.Labour <- as.character(data$Child.Labour)
data$Child.Labour[is.na(data$Child.Labour)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Child.Labour)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Child.marriage..parent.or.pregnancy

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Child.marriage..parent.or.pregnancy <- as.character(data$Child.marriage..parent.or.pregnancy)
data$Child.marriage..parent.or.pregnancy[is.na(data$Child.marriage..parent.or.pregnancy)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Child.marriage..parent.or.pregnancy)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Family.Needs

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Family.Needs <- as.character(data$Family.Needs)
data$Family.Needs[is.na(data$Family.Needs)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Family.Needs)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```


## Occurence in the household of person Medical

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Medical <- as.character(data$Medical)
data$Medical[is.na(data$Medical)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Medical)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Need.of.Care

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Need.of.Care <- as.character(data$Need.of.Care)
data$Need.of.Care[is.na(data$Need.of.Care)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Need.of.Care)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Problem.with.violence.law.recruitment

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Problem.with.violence.law.recruitment <- as.character(data$Problem.with.violence.law.recruitment)
data$Problem.with.violence.law.recruitment[is.na(data$Problem.with.violence.law.recruitment)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Problem.with.violence.law.recruitment)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Separated.Child

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Separated.Child <- as.character(data$Separated.Child)
data$Separated.Child[is.na(data$Separated.Child)] <- "No"


## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Separated.Child)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Single.Parent

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Single.Parent <- as.character(data$Single.Parent)
data$Single.Parent[is.na(data$Single.Parent)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Single.Parent)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Unaccompanied

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Unaccompanied <- as.character(data$Unaccompanied)
data$Unaccompanied[is.na(data$Unaccompanied)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Unaccompanied)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Victim.of.Violence

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Victim.of.Violence <- as.character(data$Victim.of.Violence)
data$Victim.of.Violence[is.na(data$Victim.of.Violence)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Victim.of.Violence)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)
```

## Occurence in the household of person Woman.at.Risk

```{r , echo=FALSE, warning=FALSE, cache=FALSE,comment = "", tidy = TRUE, fig.height=4, size="small"}

## chech chi sq test
data$Woman.at.Risk <- as.character(data$Woman.at.Risk)
data$Woman.at.Risk[is.na(data$Woman.at.Risk)] <- "No"

## chech chi sq test
chisq <- chisq.test(data$group_intro.goingback, data$Woman.at.Risk)
if(chisq$p.value > 0.05){
  cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e greater than the .05 significance level), therefore the variables are independent.\n"))
} else{
    cat(paste("According to the Pearson's Chi-squared test, the p-value is",format(chisq$p.value, digits=3, decimal.mark=".",  big.mark=",", scientific=FALSE)," (i.e smaller than the .05 significance level), therefore the variables are dependent.\n"))}
#chisq

cat("The graph below displays the level of correlation between variables modalities (blue positively associate, red negatively associated, the bigger the dot, the higher the correlation).\n")
corrplot(chisq$residuals, is.cor = FALSE)

```

